---
title: "RAIS electricity distribution"
author: "Beatriz Couto Ribeiro"
date: "2024-07-02"
output: html_document
editor_options: 
  chunk_output_type: console
---
---
title: "CNAE Brazil"
author: "Beatriz Couto Ribeiro"
date: "2024-06-25"
output: html_document
chunk_output_type: console
editor_options: 
  chunk_output_type: console
---

#Limpar o ambiente 
```{r}

rm(list=ls(all=T))

```

# 1. Download Data
## 1.1. Set Folder
```{r}

directory <- "C:/Users/wb618493/OneDrive - WBG/Documents/ASA - Privitazation of Distribution/Brazil/Data"

```

## 1.2. Download Packages
```{r setup, include=FALSE}
suppressMessages(memory.limit(size = NA))

if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}
suppressMessages(install_load("tidyverse", "dplyr", "ggplot2", "readr", "readxl","knitr","here", "data.table","basedosdados","bigrquery", "dbplyr","janitor","fuzzyjoin","zoo", "purrr", "stringr","DBI", "openxlsx"))

`%notin%` <- Negate(`%in%`)

```

## 1.3. set the google cloud console ID and project
```{r}

set_billing_id("rais-eletricidade-dist")

```

# 2. Download Dataset
```{r}

# firms_pe <- readRDS("PE_CNPJ_2021_2023.RDS")
# 
# sel_firms_pe <- readRDS("SELECTED_CNAE_PE_CNPJ_2021_2023.RDS")
# 
# natureza_juridica <- read.csv("natureza_juridica.csv", head = TRUE, sep=",")

```


## 2.1. Extract Dictionary 
```{r}

# dict<-read_sql(query = "SELECT * FROM `basedosdados.br_me_rais.dicionario` LIMIT 1000")

```


# Connect to RAIS database
```{r}

# Para carregar o dado direto no R
query <- "br_me_rais.microdados_vinculos"
rais_data <- basedosdados::bdplyr(query)

```

# Check data structure
```{r}

dplyr::glimpse(rais_data)

```




## 2.2. Extract data from "Firms" and "Establishment"
```{r}





```

## 2.3. Join establishment and firms in SQL query directly
```{r}

# Read the expanded query into a dataframe
merged_data <- basedosdados::read_sql(query = "SELECT e.cnpj, e.cnpj_basico, e.identificador_matriz_filial, e.situacao_cadastral, e.cnae_fiscal_principal,
       EXTRACT(year FROM e.data_inicio_atividade) AS year,
       EXTRACT(month FROM e.data_inicio_atividade) AS month,
       e.data_inicio_atividade,
       emp.natureza_juridica, 
       emp.capital_social, 
       emp.porte
FROM `basedosdados.br_me_cnpj.estabelecimentos` AS e
JOIN `basedosdados.br_me_cnpj.empresas` AS emp
ON e.cnpj_basico = emp.cnpj_basico
WHERE e.sigla_uf ='PE' 
  AND e.data_inicio_atividade >= '2021-01-01' 
  AND e.data ='2023-12-09'
  AND emp.data='2023-12-09' ")

saveRDS(merged_data,"PE_CNPJ_2021_2023.RDS")

```